### 2024-12-28 ms.qmd
Update ms.qmd

## Introduction

@@

```{r, fig-Methods}

>>>>

## Introduction
**Corticosterone is the major GC produced by
adrenal steroidogenic cells in reptiles, and an increase in
its plasma concentration is a frequent indicator of stress
(Anderson et al. 2014 General and Comparative Endocrinology). In nature,
GCs in the developing embryos seem to be largely of
maternal origin (Uller et al. 2009, The Journal of Experimental Biology) and are probably transferred to the growing oocytes through vitellogenesis (Elf et al.,
2002, 2003 General and Comparative Endocrinology (both)).**

Mechanistically, a change in body size requires
a change in cell number and/or cell size, and there is evidence that
body size and cell size undergo coordinated evolutionary (Arendt,
2007; Starostová et al., 2005; Stevenson et al., 1995) or
phenotypically plastic changes (Arendt, 2007; Czarnoleski et al.,
2013; Hessen et al., 2013).

@@
